Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-02 paper/paper.tex
pass on intro

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements entails sensible changes in runtime engines. Even
small changes can have a large impact in practice. For example, in
October 2014 a new attribute added to Array objects caused a bug that
resulted in MS Outlook web not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
bugs in JS engines is therefore an important problem. It is also
challenging because of the speed the specification
evolves~\cite{ecmas262-spec-repo} and the fact that the behavior of
various language elements is undefined~\cite{so-undefined-behavior}
(\ie{} left for the implementation to define).

%% WHAT WE DID
This paper reports the results of a study we conducted to assess
reliability of existing JS engines by leveraging implementation
diversity in two orthogonal ways. The first method considered is
\emph{test transplantation}. This method evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that when a bug is found in some
engine a test case is created and added to the regression suite. Those
test inputs often check interesting scenarios that could reveal bugs
in different engine implementations. The second method considered is
\emph{cross-engine differential testing}. This method fuzzes existing
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One
possible cause of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning}. This approach has not been
popularized, certainly because it is more challenging to fully
automate--a number of legitimate reasons exist, other than a bug, for
a test execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

@@

JavaScript engines are virtual machines that parse source code and
compile it in bytecodes. These engines implement some version of
ECMAScript\footnote{The name JavaScript still prevails today,
  certainly for historical reasons.} (\es{}), which emerged with the
goal to standardize variants of the language, such as Netscape's
JavaScript and Microsoft's JScript. The \es{} specification is
regulated by Ecma International~\cite{es6-website} under the
TC39~\cite{tc39-github} technical committee.  Every year, a new
version of the \es{} specification is produced with new features and
minor fixes. The canonical spec today is
ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
versions and supporting engines are publicly available~\cite{kangax}.

It is worth noting that undefined behavior makes differential testing
more challenging.

In the following, we briefly describe different sources of
discrepancies that can emerge across different engine implementations
as results of the active changes in the \es{} specification.

The \es{} spec uses the label ``implementation-dependent'' to indicate
cases where each engine developer can decide how to implement some
aspect of a functionality. In these cases, the behavior of some
language element may differ from engine to engine. One reason this
flexibility in the spec exists is to enable compiler
optimizations. For example, the \mcodeid{for-in} loop does not clearly
specify the iteration
order~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that~\cite{for-in-undefined}.  As another
example, the latest version of the \es{} specification states that if
the \mcodeid{Number.toPrecision()} function is called with more than
one argument, then the behavior is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like this exist in the specification.

>>>>

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with significant
penetration in the segments of web development, mobile, and even for
client and server coding for the Internet of
Things~(IoT)~\cite{simply-technologies}.

The interest of the community for the language encourages constant
improvements in its specification and implementations.  It is natural
to expect that language improvements entails sensible implementation
changes. Even small changes can have high impact. For example, in
October 2014 a new attribute added to Array objects caused a bug that
resulted in the web app for the MS Outlook Calendar not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
bugs in JS engines is therefore an important problem given the range
of applications that could be affected. It is also challenging as
specifications evolve constantly and are incomplete. More
specifically, the evolution of the \js\ specification makes it hard to
assess if a test fails because of a bug or because of some missing
feature. The publicly-available Kangax compatibility
table~\cite{kangax} highlights this problem; it relates features with
the engines that (partially) support them. For similar reason, one
could misclassify a test failure as a bug when the failure could be,
in fact, caused by some undefined behavior in the spec. To note that
many of these cases exist as it can be observed by searching for
``implementation-dependent'' in the ES6 spec
document~\cite{ecmas262-spec}.

%% WHAT WE DID
This paper reports the results of a study we conducted to assess
reliability of existing JS engines by leveraging implementation
diversity in two orthogonal ways: test transplantation and
cross-engine differential testing.  \emph{Test transplantation}
evaluates the effects that running \js{} test files from a given
engine have in detecting bugs in other engines. The intuition is that
when a bug is found in some engine a test case is created and added to
the regression suite. Those test inputs often check interesting
scenarios that could reveal bugs in different engine
implementations. \emph{Cross-engine differential testing} evaluates
the bug-finding ability of fuzzing existing
inputs~\cite{fuzz-testing-history} and then comparing the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning}. This approach has not been
popularized, certainly because it is impractical to fully automate--a
number of legitimate reasons exist, other than a bug, for a test
execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

@@

JavaScript engines are virtual machines that parse source code and
compile it in bytecodes. These engines implement some version of the
ECMAScript (\es{}), which emerged with the goal to standardize
variants of the language, such as Netscape's JavaScript and
Microsoft's JScript\footnote{The name JavaScript still prevails today,
  certainly for historical reasons.}. The \es{} specification is
regulated by Ecma International~\cite{es6-website} under the
TC39~\cite{tc39-github} technical committee.  Every year, a new
version of the \es{} specification is produced with new features and
minor fixes. The canonical spec today is
ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.

%% In the following, we briefly describe different sources of
%% discrepancies that can emerge across different engine implementations
%% as results of the active changes in the \es{} specification.

.........
A compatibility table relating features and supporting engines is
publicly available~\cite{kangax}.

Another
challenge is undefined (or implementation-dependent) behavior. The
\es{} spec uses the label ``implementation-dependent'' to indicate
cases where each engine developer can decide how to implement some
aspect of a functionality. In these cases, the behavior of some
language element may differ from engine to engine. One reason this
flexibility in the spec exists is to enable compiler
optimizations. For example, the \mcodeid{for-in} loop does not clearly
specify the iteration
order~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that~\cite{for-in-undefined}.  As another
example, the latest version of the \es{} specification states that if
the \mcodeid{Number.toPrecision()} function is called with more than
one argument, then the behavior is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like this exist in the specification.
